Fleet Definitions for Georges Bank

### 2021-03-02 docs/GBFleetDefinitions.Rmd
add figures of landings by gear type to GBFleetDefinitions.rmd

---
title: "Fleet Definitions"
author: Andy Beet
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    code_fold: hide
    number_sections: false
csl: apa-annotated-bibliography.csl
bibliography: references.bib
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

@@

```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysis on all gear types used in the Georges Bank Ecological Production unit as defined by statistical areas",eval=T,echo=F}
knitr::include_graphics("figures/dendrogram1.png")
```
Note: Low values of the agglomerative coefficient indicate tight clustering of gears types. Larger values indicate less well formed clusters.

@@

```{r dendro2,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysis on a subset of gear types in the Georges Bank Ecological Production unit as defined by statistical areas. Gear types were selected based on their contribution to 99% of landings",eval=T,echo=F}
knitr::include_graphics("figures/dendrogram2.png")
```

>>>>

---
title: "Fleet Definitions for Georges Bank"
author: Andy Beet
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    code_fold: hide
    number_sections: false
csl: apa-annotated-bibliography.csl
bibliography: references.bib
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
options(warn=-1)
```

## Spatial Extent

Statistical areas are used to define the Georges Bank footprint for pulling the landings data by gear
```{r}
crs <- 4326
# read in coastline and GB shape file
coast <- sf::st_read(here::here("gis", 'NES_LME_coast.shp'), quiet = T) %>%
  sf::st_transform(.,crs=crs)
GB_strata <- sf::st_read(here::here("gis","Statistical_Areas_2010.shp"),quiet=T) %>%
    sf::st_transform(.,crs=crs) %>%
  dplyr::filter(Id %in% c(521, 522, 523, 524, 525, 526, 538, 551, 552, 561, 562, 537) )
centroids <- sf::st_coordinates(sf::st_centroid(GB_strata))
GB_strata <- cbind(GB_strata,centroids)

#plot map
ggplot2::ggplot(data=coast) +
  ggplot2::geom_sf() +
  ggplot2::geom_sf(data=GB_strata,fill="grey") + 
  ggplot2::geom_text(data=GB_strata,ggplot2::aes(x=X,y=Y,label=Id),size=2)    +
  ggplot2::coord_sf(xlim = c(-76,-65), ylim = c(38,44))
```

## Gear Types

@@

```
```{r dendro1,out.width="100%",fig.cap="The dendrogram obtained from a nearest-neighbor, hierarchical cluster analysis on all gear types used in the Georges Bank Ecological Production unit as defined by statistical areas",eval=T,echo=F}
knitr::include_graphics("figures/dendrogram1.png")
```
Note: Low values of the agglomerative coefficient indicate tight clustering of gears types. Larger values indicate less well formed clusters.

@@

```{r dendro2,out.width="100%",fig.cap="The dendrogram obtained from a nearest-neighbor, hierarchical cluster analysis on a subset of gear types in the Georges Bank Ecological Production unit as defined by statistical areas. Gear types were selected based on their contribution to 99% of landings",eval=T,echo=F}
knitr::include_graphics("figures/dendrogram2.png")

### Species landings by gear {.tabset .tabset-pills}

Time series of species caught by each gear type

#### 01

```{r gear01,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="01")
knitr::include_graphics("figures/gear01.png")
```

#### 02
```{r gear02,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="02")
knitr::include_graphics("figures/gear02.png")
```

#### 05

```{r gear05,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="05")
knitr::include_graphics("figures/gear05.png")
```

#### 10

```{r gear10,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="10")
knitr::include_graphics("figures/gear10.png")
```

#### 12

```{r gear12,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="12")
knitr::include_graphics("figures/gear12.png")
```

#### 13

```{r gear13,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="13")
knitr::include_graphics("figures/gear13.png")
```

#### 14

```{r gear14,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="14")
knitr::include_graphics("figures/gear14.png")
```

#### 17
```{r gear17,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="17")
knitr::include_graphics("figures/gear17.png")
```

#### 18
```{r gear18,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="18")
knitr::include_graphics("figures/gear18.png")
```

#### 20
```{r gear20,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="20")
knitr::include_graphics("figures/gear20.png")
```

#### 21
```{r gear21,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="21")
knitr::include_graphics("figures/gear21.png")
```

#### 30
```{r gear30,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="30")
knitr::include_graphics("figures/gear30.png")
```

#### 37
```{r gear37,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="37")
knitr::include_graphics("figures/gear37.png")
```

#### 38
```{r gear38,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="38")
knitr::include_graphics("figures/gear38.png")
```

#### 40
```{r gear40,  echo=F, eval =T}
GBCodes %>% dplyr::filter(NEGEAR2=="40")
knitr::include_graphics("figures/gear40.png")
```
